---
title: 'Final Project Report: A Study of the Effects of Personalization on Survey Response Rates'
author: 'Carlos Eduardo Rodriguez, Sean Underwood, Winston Lin'
date: \today
output: pdf_document
---

# 1. Introduction

## Overview of Company and Business Processes



## Problem Statement/Central Question



## Previous Research on Subject



# 2. Experimental Design

## 2.1. Definition of Treatment

### Outcome of Interest



### Estimator for Treatment Effect



### Null and Alternative Hypotheses



## 2.2. Sample Design

### Sampling Method



### Block Design



### Summary Statistics



## 2.3. Assignment of Treatment

### Randomization Method



### Covariate Balance 



## 2.4. Experimental Procedure

### Instrumentation



### Data Collection



# 4. Results & Discussion

## 4.1. Experiment 1: ATG All-Hands Meeting



## 4.2. Experiment 2: PTG All-Hands Meeting



## 4.3. Meta-Analysis of Both Experiments



## 4.4. Applications and Future Research



# 6. Conclusion



# 7. Acknowledgements



# Appendices

## A. Examples of Emails for Treatment and Control Groups


## C. R Code for Experiment

### Sample Data



### Anonymization

```{r}

```

### Block Randomization

```{r}

```


### Analysis

```{r}

```
