---
title: 'Final Project Report: A Study of the Effects of Personalization on Survey Response Rates'
author: 'Carlos Eduardo Rodriguez, Sean Underwood, Winston Lin'
date: \today
output: pdf_document
header-includes:
    - \usepackage{caption}
---

\captionsetup[table]{labelformat=empty}

```{r}
library(RCurl)
library(data.table)
library(knitr)
library(ri)
library(stargazer)

RI_ITERATIONS = 1000
```

# 1. Introduction

## Overview of Company and Business Processes



## Problem Statement/Central Question



## Previous Research on Subject



# 2. Experimental Design

## 2.1. Definition of Treatment

### Outcome of Interest



### Estimator for Treatment Effect



### Null and Alternative Hypotheses



## 2.2. Sample Design

### Sampling Method



### Block Design



### Summary Statistics



## 2.3. Assignment of Treatment

### Randomization Method



### Covariate Balance 



## 2.4. Experimental Procedure

### Instrumentation



### Data Collection


# 3. Pilot Study

We also performed a pilot study with help from the datascience@berkeley staff. They were conducting an email survey of the MIDS student body to study engagement with the _Applications in Data Science_ webinar series, and graciously agreed to help us test some of our procedures on this survey.

## 3.1 Pilot Design

The treatment in the pilot survey was roughly the same as in the primary survey, with control paricipants receiving an email with a generic salutation and treatment participants receiving a personalized salutation that included their first name. In order to remain consistent with existing precedent, the exact wording of the email saluatation was slightly different: "Hello Everyone" for control, and "Hello [studen's first name]" for treatment.

One signifcant departure from the primary experiment's design was that we did not use block random assignment for the pilot study. Gender was not included because we did not have easy access to that information, and department was not included because that variable does not apply in this case. This did unfortunately limit our ability to use the pilot as a full dress rehearsal, since it involved significantly less logistic complexity.

# 4. Results & Discussion

```{r}
# Function to calcualte ATE, P-value and 95% confidence interval
# arguments:
#  Z: Vector of treatment assignment
#  Y: Vector of outcomes
#  block (optional): Vector of block numbers
ri.test = function(Z, Y, block=NULL) {
  perms = genperms(Z, blockvar=block, maxiter=RI_ITERATIONS)  # Permutations of treatment assignment
  probs = genprobexact(Z, blockvar=block) # Probability of treatment assignment
  ate = estate(Y, Z, prob = probs)
  
  # Getting p-value under sharp null
  ys.null = genouts(Y, Z, ate=0) # Potential outcomes under sharp null
  distout.null = gendist(ys.null, perms, prob = probs) # Outcome distribution under sharp null
  p = dispdist(distout.null, ate, display.plot=FALSE)$two.tailed.p.value
  
  # Getting 95% CI
  ys.alt = genouts(Y, Z, ate=ate) # Potential outcomes under alternative hypothesis
  distout.alt = gendist(ys.alt, perms, prob = probs) # Outcome distribution under alternative
  ci = dispdist(distout.alt, ate, display.plot=FALSE)$quantile
  
  list(ate = ate, p = p, ci = ci)
}
```


## 4.1 Pilot

```{r}
# Setting up pilot data
dt.pilot = n.treat = 134
n.control = 133
n.treat.responded = 6
n.control.responded = 4

dt.pilot = data.table(
    treat = c(rep(1, n.treat), rep(0, n.control)),
    responded = c(rep(1, n.treat.responded),                # treat responses
                  rep(0, n.treat - n.treat.responded),      # treat non-responses
                  rep(1, n.control.responded),              # control responses
                  rep(0, n.control - n.control.responded))  # control non-responses
)

dt.pilot.summary = dt.pilot[, 
                            .(.N, 
                              Responses = sum(responded), 
                              Rate = sum(responded) / .N), 
                            by=treat]
```

```{r, results='asis'}
# Printing pilot summary data
kable(dt.pilot.summary, digits=3, caption = "Pilot Survey Results", format="pandoc")
```

```{r, results='asis'}
# Pilot data analysis using regression
lm.pilot = lm(responded ~ treat, data=dt.pilot)
stargazer(lm.pilot, type='latex', title="Regression: Pilot Survey")
```

```{r}
# Pilot data analysis using randomization inference
ri.test(dt.pilot$treat, dt.pilot$responded)
```



--------------------------------
Group         N  Responses  Rate
----------- --- ---------- ----- 
Treatment:  134          6  4.5%

Control:    133          4  3.0%

Total:      267         10  3.7%
--------------------------------


## 4.2 Experiment 1: ATG All-Hands Meeting

```{r}
#csv = getURL('https://raw.githubusercontent.com/winlingit/w241-project-csw/master/rcode/atg_results.csv')
#dt = data.table(read.csv(textConnection(csv)))
dt.atg.sum=fread('~/Documents/Berkeley/241/Final\ Project/w241-project-csw/rcode/atg_results.csv')
dt.atg.sum[Female == 0, Gender := 'M']
dt.atg.sum[Female == 1, Gender := 'F']
dt.atg.sum[, Y := Responses / N]
```

```{r, results='asis'}
# Covariate/block table
atg.stats = dt.atg.sum[order(Org, Region, Gender, treat), .(Org, Region, Gender, Treat=treat, N)]
kable(atg.stats, digits=2, caption = "ATG Survey Blocks", format = 'pandoc')
```

```{r}
# Results summary
atg.results = dcast(dt.atg.sum, 
                    blocknum + Org + Region + Gender ~ treat, 
                    value.var= c('N', 'Responses', 'Y'))

atg.results = atg.results[, 
                          .(Org, Region, Gender, 
                            'N' = N_0 + N_1, '# Treat' = N_0, '# Control' = N_1, 
                            'Y(0)' = Y_0, 'Y(1)' = Y_1, ATE = Y_1 - Y_0)]

kable(atg.results, digits=2, caption = "ATG Survey Results", format="pandoc")
```

```{r}
# Data reshaped to one row per partcipant.
dt.atg = dt.atg.sum[rep(seq(.N), N), 
                    .(CollectorId, blocknum, Org, Region, Female, Treat = treat, Responses), 
                    with = T]  # expand table to 352 rows

dt.atg[ , 
        Responded := c(rep(1, max(Responses)), 
                       rep(0, .N - max(Responses))), 
        by = CollectorId]  # add var for responded
dt.atg.sum$Responses == dt.atg[ , sum(Responded), by = CollectorId]$V1  # checksums for total responses for each collector
```

```{r}
# Analysis using regression
lm.atg = lm(Responded ~ Treat, data=dt.atg)
stargazer(lm.atg, type='text', title="Regression: ATG Survey")
```

```{r}
# Analysis using randomizatino inference (not taking blocks into account)
ri.test(dt.atg$Treat, dt.atg$Responded)
```

```{r}
# Analysis using randomizatino inference (with blocks)
ri.test(dt.atg$Treat, dt.atg$Responded, block=dt.atg$blocknum)
```

\pagebreak

## 4.3 Experiment 2: PTG All-Hands Meeting


```{r}
dt.ptg=fread('~/Documents/Berkeley/241/Final\ Project/w241-project-csw/rcode/ptg_assignment.csv')
dt.ptg[Female == 0, Gender := 'M']
dt.ptg[Female == 1, Gender := 'F']
dt.ptg = dt.ptg[order(Org, Region, Gender, Treat), .(Org, Region, Gender, Treat, N)]
```

```{r}
kable(dt.ptg, digits=2, caption="PTG Survey Blocks", format="pandoc")
```


## 4.3. Meta-Analysis of Both Experiments



## 4.4. Applications and Future Research



# 6. Conclusion



# 7. Acknowledgements



# Appendices

## A. Examples of Emails for Treatment and Control Groups


## C. R Code for Experiment

### Sample Data



### Anonymization

```{r}

```

### Block Randomization

```{r}

```


### Analysis

```{r}

```
